Viscous Transport in Eroding Porous Media

### 2019-08-14 docs/transport/erosion_transport.tex
started to rewrite the introduction

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Flow-induced erosion deteriorates and reshapes solid material over a
range of scales.  At small scales, such as in groundwater flow,
fluid-mechanical erosion significantly alters the geometry, and
ultimately changes the process of transport through the media.  This
paper extends a quadrature method first outlined by Barnett, Wu, and
Veerapaneni~\cite{bar-wu-vee2015} to simulate dense packings of eroding
bodies, and then studies coarse-grained variables to characterize
transport in eroded geometries.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Flow in many natural occurring geometries involves flows that vary over
many orders of magnitude.  Porous media are one such geometry where the
length scales in a single geometry can vary from $10^{-6}m$ to
$10^{-1}m$~\cite{mil-chr-imh-mob-ped1998}.  Simulating such a wide range
of length scales is impractical, and constitutive laws that link the
microscopic scale to macroscopic scale must be
developed~\cite{mil-chr-imh-mob-ped1998}.  However, to find closure
formulas, accurate simulations at microscopic scales must be performed
and analyzed.
\todo[inline]{Talk about aquifers here}

At microscopic scales, the Reynolds number is small, and the fluid is
governed by the incompressible Stokes equations (for example, see
~\cite{hym-den-hag-kan2019, den-ica-hid2018, bar-mar-vee-zha2018})
\begin{align}
  \mu \Delta \uu = \nabla p, \quad \nabla \cdot \uu = 0,
\end{align}
where $\uu$ is the velocity, $p$ is the pressure, and $\mu$ is the fluid
viscosity.  Even though the pore-scale geometry can be complex, the
Stokes equations can be accurately solved in these complex geometries by
using an integral equation method.  In addition to being accurate and
able to resolve complex geometries, integral equation methods
automatically satisfy mass conservation, result in a dimension
reduction, and can be solved in optimal time by using a fast summation
method.

Once the governing equations are solved, the flow can characterized
statistically~\cite{}.  For example, dispersion is described by the
second moment of particle trajectories.  Other measures of the flow
involve computing distributions of the velocity on Eulerian
grids~\cite{} and Lagrangian grids~\cite{}, calculating the
distribution of the time required for a trajectory to pass from the
inlet to the outlet of the geometry, and by computing the length of
streamlines passing from the inlet to the outlet.

A common necessity to describe the microscopic scale is describe
transport through the complex geometry.  Depending on the application,
the transport may be passive and be described by pure
advection~\cite{}, it may describe a concentration field, such as a
contaminant, and be governed by a finite Peclet number
advection-diffusion equation, or they may stochastic and be described
using a random walk~\cite{}.  In this work, we focus on pure
advection so that we are interested in passive tracers whose
trajectories, or equivalently, the streamlines, are governed by
\begin{align}
  \frac{d\ss}{dt} = \uu(\ss,t), \quad \ss(0) = \ss_0.
\end{align}

In many applications, the fluid transport continuously changes the
pore structure.  This is particularly common in geophysical flows where
erosion alters the porous matrix.

Flow-induced erosion deteriorates and reshapes solid material over a
range of scales.  At small scales, such as in groundwater flow,
fluid-mechanical erosion significantly alters the geometry, and
ultimately changes the process of transport through the media.  This
paper extends a quadrature method first outlined by Barnett, Wu, and
Veerapaneni~\cite{bar-wu-vee2015} to simulate dense packings of eroding
bodies, and then studies coarse-grained variables to characterize
transport in eroded geometries.
